---
title: "Week 6 Assignment"
author: "Christina"
date: "Oct 3, 2015"
output: html_document
---

### Airline Delay Analysis  
#### Data transformation with tidyr and dplyr  
```{r message=FALSE}
#load data
setwd('C:/Users/Christina/Documents/GitHub/IS')
df<-read.csv("airline2.csv", na.strings = "")
data<-df[rowSums(is.na(df))!=7, ]
names(data)[1:2]<-c('airline','status')
library('zoo')
data$airline<-na.locf(data$airline)

#transform wide to long format 
library(tidyr)
dflong <- data %>% gather(airport, number, -airline, -status)
library(dplyr)
#high lever statistics
delayed<-select(filter(dflong, status == 'DELAYED'),-status)
arrange(delayed, airline,desc(number))
#average number of delays by airline
summarise(group_by(delayed, airline),airports = n(),avg = mean(number))
sum<-summarise(group_by(dflong, airline, status),airports = n(),total = sum(number))
#total delay rate
stats<-sum %>% group_by(airline) %>% mutate(pct=(100*total)/sum(total))
select(filter(stats, status=='DELAYED'),-status, -airports)
```
**Alaska appears to have less number of delayed flights, but overall higher delay rate.**  

### What happens at each airport?
```{r}
#calculate percentage of delays at each airport
airports<-filter(dflong %>% group_by(airline, airport) %>% mutate(pct=(100*number)/sum(number)), status == 'DELAYED')
```
**Barplot of delays by airline:**  
```{r, message=FALSE, echo=FALSE}
library(ggplot2)
library(ggthemes)
g2<-ggplot(airports, aes(x=airline,y=pct, fill=airline))+geom_bar(position="dodge", stat = "identity") + facet_wrap(~airport)
g2<-g2+labs(title="Delays at each airport", x="Airline", y="Delay Rate (%)"）
g2+theme_gdocs()
```

** It appears that at every airport, Alaska is less likely to be delayed. Recall that overall, Alaska has a highter delay rate! How is this possible?**  

### Is airport a factoring variable?  
**Are some airports notorious for congestion?** 
```{r, message=FALSE}
arrange(summarise(group_by(delayed, airport),total = sum(number)),desc(total))
```

**Phoenix and Seattle have large volumes of delayed flights.**  

```{r, message=FALSE, echo=FALSE}
g5<-ggplot(delayed, aes(x=airport,y=number))
g5<-g5+geom_point(aes(color=airline))
g5<-g5+labs(title="Delay at Airports", x="Airport", y="Num of Delays", color="Airline")
g5+theme_gdocs()
```
  
**AM West has a lower delayed rate overall, because it performed fairly well in Phonenix - about 75% of its total flights are on time.**  
