---
title: "Week 4"
author: "Christina"
date: "September 16, 2015"
output: html_document
---

### Chapter 8: Regular Expressions
####4. 
(a)  
[0-9]: match any single digit  
+: match one or more times  
\\$ match dollar sign  
Example: 
```{r}
library(stringr)
obj <- "1$ 12$  1234$"
unlist(str_extract_all (obj, "[0-9]+\\$"))
```

(b)  
"\\b" match empty string at either edge (boundary) of a word  
[a-z]: match any single lower case ascii character  
{1,4}: match [a-z] at least 1 time but no more than 4 times  
Example:   
```{r}
obj <- "a bc def ghij klmno"
unlist(str_extract_all (obj, "\\b[a-z]{1,4}\\b"))
```

(c) "." match any single character  
"*" repeats the "." 0 or more times  
"?" is a qualifier that matches the preceding pattern 0 times or once  
"\\.txt$" matches the literal ".txt" at the end of line  
Example:  
```{r}
obj <- ".txt b 52.txt d&e.txt"
unlist(str_extract_all (obj, ".*?\\.txt$"))
```

(d) This expression matches single digits exactly twice; followed by "/", followed by single digits exactly twice, followed by "/", followed by single digits exactly four times  
Example:   
```{r}
obj <- "09/16/2015 99/99/1999  1234/56/78"
unlist(str_extract_all (obj, "\\d{2}/\\d{2}/\\d{4}"))
#Note: This is not a good regex for dates. [01]\d[- /.][0-3]\d[- /.]\d\d is better, though not perfect.
```

(e) This expression matches character "<", followed by (.+?) grouping: match any single charcter, one or more times, and the preceding patten is optional.  
This is followed by character ">", followed by any single character, one or more times, optional.  
This is followed by "<", followed by the same pattern as enclosed in the parenthesis before, then "/>".  
Example: 
```{r}
obj <- "<b>Week 4</b> <b>2015</b> <title></title> <></>" 
unlist(str_extract_all (obj, "<(.+?)>.+?</\\1>")) #Note: The tag cannot be empty.
```

####5.  
[:digit:]{1,}[$]  
```{r}
obj <- "1$ 12$  1234$"
unlist(str_extract_all (obj, "[:digit:]{1,}[$]"))
```

####6.
(a)
```{r}
mail <- "chunkylover53[at]aol[dot]com"
mail <- sub("[at]", "@", mail, fixed=TRUE) 
email <- sub("[dot]", ".", mail, fixed=TRUE) 
email
```
(b)  
"[:digit:]" will extract a single digit. To extract the digits we need to match one or more times:  
```{r}
unlist(str_extract_all(email, "[:digit:]+"))
```
(c)  
"\\D" will extract non-digits. The correct predifined symbol is \\d, matched one or more times.
```{r}
unlist(str_extract_all(email, "\\d+"))
```